Non-convergence in iterative imputation

### 2025-04-22 Manuscript/manuscript.qmd
add miss pat

```{r patterns, echo=FALSE, eval=FALSE}
source("../R/generate_datasets.R")
pat <- create_patterns(3)
d <- dat[1:10,]
is.na(d) <- pat == 1
d
ggmice::plot_pattern(d)
```

>>>>

```{r patterns, echo=FALSE}
source("../R/generate_datasets.R")
pat <- create_patterns(3)
is.na(pat) <- pat == 1
pat
ggmice::plot_pattern(pat, caption = FALSE) +
  theme(axis.text.x=element_blank(), 
      axis.ticks.x=element_blank(), 
      axis.text.y=element_blank(), 
      axis.ticks.y=element_blank(),
      axis.text = element_blank()) +
  theme_void()
```
